Instructions for developing new pages for the MarineOmics webpage

### 2023-12-15 DRAFT_DNA_methylation.Rmd
adding explanation of BSsnper

One way to do this is using BS-Snper (@10.1093/bioinformatics/btv507). <https://github.com/hellbelly/BS-Snper>. In short one could merge all BAM files from experiment run BS-Snper, filter out C->T SNPS then use this to remove loci.

@@

>>>>

One way to do this is using BS-Snper (@10.1093/bioinformatics/btv507). <https://github.com/hellbelly/BS-Snper>. This program finds SNPs in Bisulfite treated alignment files. The bash code below represents steps to identify SNPS and create a list of all C->T SNPS.

@@

The resulting could be used to mask the genome and the entire process described abo
